taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-04-09 paper/manuscript.Rmd
fix case in input col

```{r message=FALSE, include = FALSE}
library(kableExtra)
library(magrittr)
library(tidyverse)
library(taxadb)

pkgconfig::set_config("dplyr::na_matches" = "never")

@@

```{r}
by_rank("Aves", rank="class", provider = "col") %>% head(5)
```

>>>>

```{r message=FALSE, include = FALSE}
library(kableExtra)
library(magrittr)
library(tidyverse)
library(taxadb)
library(printr)
pkgconfig::set_config("dplyr::na_matches" = "never")

@@

```{r}
by_rank("Aves", rank="class", provider = "col") %>%
  ## some example columns
  select(taxonID, taxonomicStatus, taxonRank, genus, specificEpithet) %>% 
  head(5)

We can inspect all columns:

```{r}
by_rank("Aves", rank="class", provider = "col") %>% names()
```

Note that each of these terms are defined by
